The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-11-25 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated paper as per referee's comments

For example, \emph{Hilbert-Kunz multiplicity} is realized in this way. 
Given an ideal $I$ of a ring $R$ of characteristic $p>0$, $I^{[p^e]}$ denotes the $p^e$-th Frobenius power of $I$, that is, the ideal generated by the $p^e$-th powers of the elements of $I$. If $R$ has dimension $d$ and $\lambda\left(R/I^{[p^e]}\right)$ denotes the length of $R/I^{[p^e]}$, the limit of $\frac{\lambda\left(R/I^{[p^e]}\right)}{p^{ed}}$ is the Hilbert-Kunz multiplicity of $R$ with respect to $I$.

>>>>

For example, \emph{Hilbert-Kunz multiplicity} is realized in this way. 
Suppose that $I$ is an ideal of a ring $R$ of characteristic $p>0$.
Given an integer $e \geq 1$, 
$I^{[p^e]}$ denotes the $p^e$-th Frobenius power of $I$, that is, the ideal generated by the $p^e$-th powers of the elements of $I$. 
If $R$ has dimension $d$ and $\lambda\left(R/I^{[p^e]}\right)$ denotes the length of $R/I^{[p^e]}$, 
then the limit of $\lambda\left(R/I^{[p^e]}\right)/p^{ed}$ as $e$ grows is the Hilbert-Kunz multiplicity of $R$ with respect to $I$.
